An Introduction to Return Oriented Programming

### 2023-02-17 paper.tex
changes

%%%% 6. ABSTRACT %%%%
\begin{abstract}
  In this paper we introduce the concept, demonstrate an attack and talk about the different protection mechanisms of Return Oriented Programming. ROP is a buffer overflow exploitation technique developed in 2007. Under certain circumstances it can provide arbitrary code execution on assembly level. Modern 64 Bit binaries are decently secure against ROP with ASLR and stack protections enabled. 32 Bit binaries or binaries compiled for non PC systems may not provide the same protection though and may be vulnerable to ROP.
\end{abstract}

>>>>

%%%% 6. ABSTRACT %%%%
\begin{abstract}
ROP is a buffer overflow exploitation technique developed in 2007. Under certain circumstances it can provide arbitrary code execution on assembly level, because of that it is a devastating technique for black-hats. Modern 64 Bit binaries are generally decently secure against ROP with ASLR and stack protections enabled. 32 Bit binaries or binaries compiled for non PC systems may not provide the same protection though and may be vulnerable to ROP. 
\end{abstract}
